Blockchain System

### 2020-11-18 papers/execution-model/model.tex
Add files via upload

\begin{definition}%[Account]
  An \emph{account} is a tuple $\langle
  %\ALS,
  \PAK, \PUK
  %, \PKH
  \rangle $, where
  % $\ALS$ is the alias of the account,
  $\PAK$ is its private key and $\PUK$ is its public key.
  % and $\PKH$ is its public key hash . 
\end{definition}

% \begin{definition}%[Contract]
%   An \emph{contract} is a tuple $\langle
%   % \ALS,
%   \PUH, \CODE \rangle $, where
%   % $\ALS$ is the alias of the contract, 
%   $\PUH$ is its public hash, and
%   $\CODE$ is the code of the contract. 
% \end{definition}

\begin{definition}%[Operation]
  \emph{Operations} are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [\ACCOUNTS, \OPERATIONS]$ where $\ACCOUNTS$ is a set of
  accounts and
  $\OPERATIONS$ a set of operations.
\end{definition}

@@

\begin{definition}%[Manager]
A \emph{manager} manages a single account. It is represented by a
tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
is a boolean value.  
\end{definition}

@@

\begin{definition}%[Query]
A \emph{query} is defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE {\PKH / \PUH}
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETPUBLICKEY\PKH
  \\&\mid \GETCOUNTER\PKH
\end{align*}

%$\mid$ get delegate for $\PKH$
%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\PKH$
%\\$\mid$ get balance for $\PKH$

@@

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}%[Pending operation]
A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}%[Accepted operation]
An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

@@

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
\end{enumerate}
\end{definition}

@@

  % \inferrule[Node-Originate]
  % {\CHECKACC (\PUK, \ACCOUNTS) \\
  %   % \CHECKID (\ID, \CONTRACTS) \\
  %   \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
  % }{
  %   [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
  %   \NodeTrans 
  %   [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
  % }
  %
  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}

@@

% Rule 1 [proposal]:
%
% \begin{mathpar}
%   \inferrule[Xfer-Propose]{
%     \CHECKACC (\PKH, \ACCOUNTS)
%   }{
% \langle[\ACCOUNTS, \OPERATIONS,
%         \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
%         \TIME]\rangle \rightarrow \\
%         \langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ) ::
%         \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
%         \CONTRACTORS, \TIME]\rangle      }
% \end{mathpar}

Rule 2 [injected]:

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\\\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'/\PUH}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

\subsection{Smart Contracts}
~\\
A. Originate
~\\
~\\
% Rule 1 [proposal]:

% \begin{equation}{}
%   \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
%   {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
%         [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
%         \rightarrow \langle$[\ACCOUNTS, 
%         (originate contract ${id}$ transferring} \\
%   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
% ~\\
% ~\\
Rule 2 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME) 
  }{
    \Angle{[
      \ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 4 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME < 60
  }{
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \SystemTrans \\
    \langle
      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
      \\
      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} :: \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
    \rangle
  }
\end{mathpar}

>>>>

\begin{definition}%[Account]
  An implicit \emph{account} is a tuple $\langle
  %\ALS,
  \PAK, \PUK
  %, \PKH
  \rangle $, where
  $\PAK$ is its private key and $\PUK$ is its public key.
\end{definition}

\begin{definition}%[Operation]
  \emph{Operations} are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\PARAMETER]\NTEZ\PUK\ADDR\MTEZ
    \\&\mid \ORIGINATE\NTEZ\PUK\CODE\INIT\MTEZ
  \end{align*}
  where \NTEZ\ and \MTEZ\ are amount of Tez, \ADDR\ is either a public key for an implicit account  or a public hash for a smart contract,  \PARAMETER\ is an argument passed to the smart contract's script, which is emtry if it is a transfer to an implicit account, \CODE\ is a script of the smart contract, \INIT\ is an initial value of the contract's storage.
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [\ACCOUNTS, \OPERATIONS]$, where $\ACCOUNTS$ is a set of
  accounts and
  $\OPERATIONS$ is a set of operations.
\end{definition}

@@

\begin{definition}%[Manager]
A \emph{manager} manages a single implicit account. It is represented by a
tuple $\langle  \PUK, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\BAL$ is its
balance and $\COU$ is its counter whose form is a value-flag pair $(n, b)$, where $n$, which is called the value of the counter,  is a natural number and ${b}$, which is called the flag of the counter, is a boolean value.  
\end{definition}

@@

\begin{definition}%[Query]
A \emph{query} is defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE\ADDR
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETCOUNTER\PUK
\end{align*}

@@

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}%[Pending operation]
A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}%[Accepted operation]
An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
$\TIME'$ is the time when it was included in the blockchain. 
\end{definition}

@@

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK = c.\PUK$.
\end{enumerate}
\end{definition}

@@

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}

@@

Rule 1 [injected]:

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    %\NEG\ \CHECKCOU (\MANAGERS, \PUK)\\
    %\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of public key]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUB (\MANAGERS, \PUK') \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

\subsection{Smart Contracts}
A. Originate
~\\
~\\
Rule 1 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
  }{
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of code]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPRG (\CODE, \STRING) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME < 60
  }{
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']
    \SystemTrans
      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \UPDATESTORAGE(\STRING, '', '')} :: \CONTRACTORS, \TIME'+1]
  }
\end{mathpar}
~\\
~\\
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
}{
    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']
    %}
    \BlockTrans
    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
    % }
}
\end{mathpar}
~\\
~\\
B. \textbf{Transfer}
~\\
~\\
Rule 1 [injected]:
\begin{mathpar}
  \inferrule[Block-Call]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME)
  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    \SystemTrans \\
    [\ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
\end{mathpar}
~\\
~\\
Rule 2 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    \SystemTrans
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
\end{mathpar}
~\\
~\\
Rule 3 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    \SystemTrans
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
\end{mathpar}
~\\
~\\
Rule 4 [rejected of public hash]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUH (\CONTRACTORS, \PUH)\\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    \SystemTrans
    [\ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
\end{mathpar}
~\\
~\\
Rule 5 [rejected of argument]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)\\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
